Individual Differences Across Visual Search Tasks

### 2017-02-07 writeup/manuscript.tex
note on half/half test-retest
note on planned sample size

\subsection{Participants}
We aim to find 64 participants to volunteer to take part in this experiment. Participants will be students from the University of Aberdeen, and will be compenstate £x.xx for their time. Sample size was determined in part due to constraints with counter-balancing <expand>.

@@

The study consists of three different paradigms from the visual search literature in which strong individual differences were found \citep{nowakowsak2017, irons-leber2016, kristjansson2014}.
{}
\subsubsection{A: Split-half array search}

>>>>

\subsection{Participants}
We aim to find 64 participants to volunteer to take part in this experiment. Participants will be students from the University of Aberdeen. Some will be compensated with course credit and some will be paid £10 for their time*. Sample size was determined in part due to constraints with counter-balancing; there are 16 different possible orders of tasks/conditions; we will run four participants in each order for a total of 64. All participants will sign a form giving informed consent. The study has already been approved by the University of Aberdeen Psychology Ethics Committee

@@

The study consists of three different paradigms from the visual search literature in which strong individual differences were found \citep{nowakowsak2017, irons-leber2016, kristjansson2014}. The \cite{nowakowsak2017} experiment will be carried out twice to give us an estiamte of how consistent participants are in their search strategy. Both sessions were indentical.
